Tabular Constraint Learning

### 2016-04-14 Paper/ECAI/tabular.tex
adding comments

\subsection{Constraint ordering} $\constrainttorder(\constraints,\dependencies)$ uses the DAG~\dependencies in Figure \ref{fig:learning_order} in the following way: all constraints are generated in the topological order of~\dependencies.
Solid edges point from more general to more specific constraints.
Therefore, if there is a solid edge from constraint~$C_1$ to constraint~$C_2$, then a set of subgroups satisfying~$C_2$ must contain the subgroups satisfying~$C_1$.

@@

\section{Evaluation}
In this section we experimentally validate our approach.
We studied various questions, most notably with what accuracy our algorithm can find essential constraints.

>>>>

\subsection{Constraint ordering} 
\sergey{refinement operator, we need emphasize it}
$\constrainttorder(\constraints,\dependencies)$ uses the DAG~\dependencies in Figure \ref{fig:learning_order} in the following way: all constraints are generated in the topological order of~\dependencies.
Solid edges point from more general to more specific constraints.
Therefore, if there is a solid edge from constraint~$C_1$ to constraint~$C_2$, then a set of subgroups satisfying~$C_2$ must contain the subgroups satisfying~$C_1$.

@@

\section{Evaluation}
\sergey{we need to add a summary of the dataset, avg number of constraints, cells, rows, columns}
In this section we experimentally validate our approach.
We studied various questions, most notably with what accuracy our algorithm can find essential constraints.
